Add Plant Functional Type (PFT) labels

### 2021-04-23 R/add_plant_functional_type.Rmd
sort the modis labels

```{r check_col_pftMRA}
# unique values in the pft_MRA column: 
print(unique(taxon_pft_lookup$pft_MRA))
```
```{r check_col_pftMODIS}
# unique values in the pft_MODIS column: 
print(unique(taxon_pft_lookup$pft_MODIS))
```
```{r check_col_phenology}
# unique values in the phenology column: 
print(unique(taxon_pft_lookup$phenology))
```
```{r check_col_leafType}
# unique values in the leafType column: 
print(unique(taxon_pft_lookup$leafType))
```
```{r check_col_growthForm}
# unique values in the growthForm column: 
print(unique(taxon_pft_lookup$growthForm))
```

>>>>

```{r check_col_pftMRA}
# unique values in the pft_MRA column: 
print(unique(taxon_pft_lookup$pft_MRA))
```
```{r check_col_pftMODIS}
# unique values in the pft_MODIS column: 
print(sort(unique(taxon_pft_lookup$pft_MODIS)))
```
```{r check_col_phenology}
# unique values in the phenology column: 
print(unique(taxon_pft_lookup$phenology))
```
```{r check_col_leafType}
# unique values in the leafType column: 
print(unique(taxon_pft_lookup$leafType))
```
```{r check_col_growthForm}
# unique values in the growthForm column: 
print(unique(taxon_pft_lookup$growthForm))
```
